quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-19 paper-quollr.Rmd
Updated Figure 6 HTML output

```{r limb-rmse, fig.cap="Assessing which of the 6 NLDR layouts on the limb muscle data is the better representation using RMSE for varying binwidth ($a_1$). Colour  used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-f). Layout d is perform well at large binwidth (where the binwidth is not enough to capture the data struture) and poorly as bin width decreases. Layout f is the best choice.", fig.pos='H', out.width="100%"}

free(error_plot_limb) + wrap_plots(
  nldr1, nldr2, nldr3, 
  nldr4, nldr5, nldr6, ncol = 2)
```

@@

@@

langevitour::langevitour(df_model_data_limb_n[1:(length(df_model_data_limb_n)-1)],
                         lineFrom = trimesh_data_limb$from,
                         lineTo = trimesh_data_limb$to,
                         group = factor(df_model_data_limb_n$type,
                                        c("0", "1", "2", "3", "4", "5", "6", "model")),
                         levelColors = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494', "#000000"))
```

@@

@@

langevitour::langevitour(df_model_data_limb_n[1:(length(df_model_data_limb_n)-1)],
                         lineFrom = trimesh_data_limb$from,
                         lineTo = trimesh_data_limb$to,
                         group = factor(df_model_data_limb_n$type,
                                        c("0", "1", "2", "3", "4", "5", "6", "model")),
                         levelColors = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494', "#000000"))
```

```{r model-limb, fig.cap="Compare the published $2-\\text{D}$ layout (Figure \\@ref(fig:limb-rmse) b) and the $2-\\text{D}$ layout selected (Figure \\@ref(fig:limb-rmse) f) by RMSE plot (Figure \\@ref(fig:limb-rmse)) from the tSNE, UMAP, PHATE, TriMAP, and PaCMAP with different (hyper)parameters. The Limb muscle data ($n =  1067$) has seven close different shaped clusters in $10\\text{-}D$.", out.width="100%", fig.width=15, fig.height=10}

@@

>>>>

```{r limb-rmse, fig.cap="Assessing which of the 6 NLDR layouts on the limb muscle data is the better representation using RMSE for varying binwidth ($a_1$). Colour  used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-f). Layout d is perform well at large binwidth (where the binwidth is not enough to capture the data struture) and poorly as bin width decreases. Layout f is the best choice.", fig.pos='H'}

error_plot_limb + 
  wrap_plots(nldr1, nldr2, nldr3, 
  nldr4, nldr5, nldr6, ncol = 2) 
```

@@

trimesh_limb_int <- ggplotly(trimesh_limb, 
                                width = "350", 
                                height = "350", 
                                tooltip = "none") |>
  config(
    staticPlot = TRUE,        # Disables all interactivity (no hover, zoom, pan)
    displayModeBar = FALSE,   # Hides the plotly toolbar
    editable = FALSE,         # Disables annotations and editing
    showTips = FALSE,         # Removes tooltip on hover
    displaylogo = FALSE,      # Hides plotly logo
    responsive = FALSE        # Disables responsive resizing
  )

@@

limb_highd_vis <- langevitour::langevitour(df_model_data_limb_n[1:(length(df_model_data_limb_n)-1)],
                         lineFrom = trimesh_data_limb$from,
                         lineTo = trimesh_data_limb$to,
                         group = factor(df_model_data_limb_n$type,
                                        c("0", "1", "2", "3", "4", "5", "6", "model")),
                         levelColors = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494', "#000000"),
                         enableControls = FALSE,
                         width = "421px", height = "421px")
```

@@

trimesh_limb_best_int <- ggplotly(trimesh_limb_best, 
                                width = "350", 
                                height = "350", 
                                tooltip = "none") |>
  config(
    staticPlot = TRUE,        # Disables all interactivity (no hover, zoom, pan)
    displayModeBar = FALSE,   # Hides the plotly toolbar
    editable = FALSE,         # Disables annotations and editing
    showTips = FALSE,         # Removes tooltip on hover
    displaylogo = FALSE,      # Hides plotly logo
    responsive = FALSE        # Disables responsive resizing
  )

@@

limb_highd_vis_best <- langevitour::langevitour(df_model_data_limb_n[1:(length(df_model_data_limb_n)-1)],
                         lineFrom = trimesh_data_limb$from,
                         lineTo = trimesh_data_limb$to,
                         group = factor(df_model_data_limb_n$type,
                                        c("0", "1", "2", "3", "4", "5", "6", "model")),
                         levelColors = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494', "#000000"),
                         enableControls = FALSE,
                         width = "421px", height = "421px")
```

```{r model-limb, fig.cap="Compare the published $2-\\text{D}$ layout (Figure \\@ref(fig:limb-rmse) b) and the $2-\\text{D}$ layout selected (Figure \\@ref(fig:limb-rmse) f) by RMSE plot (Figure \\@ref(fig:limb-rmse)) from the tSNE, UMAP, PHATE, TriMAP, and PaCMAP with different (hyper)parameters. The Limb muscle data ($n =  1067$) has seven close different shaped clusters in $10\\text{-}D$.", out.width="100%", fig.width=15, fig.height=10, eval=knitr::is_latex_output()}

@@

htmltools::browsable(
  tagList(
    tags$div(
      id = "fig-limb-model",  # This is the anchor
      crosstalk::bscols(
        htmltools::div(
          style = "display: grid; grid-template-columns: 1fr 1fr;",
          trimesh_limb_int,
          htmltools::div(style = "margin-top: 13px;", limb_highd_vis),
          trimesh_limb_best_int,
          htmltools::div(style = "margin-top: 13px;", limb_highd_vis_best),
        ),
        device = "xs"
      ),
      tags$p(tags$strong("Figure 6:"), "Compare the published.")
    )
  )
)
